\chapter{Agent performance}

The report should include a section documenting the tests you performed to improve the negotiation strength of your agent. You must include scores of various tests over multiple sessions that you performed while testing your agent. Describe how you set up the testing situation and how you used the results to modify your agent.
(Note: to keep the report readable, place the test results in the appendix and only repeat the most important results in this text.)

\section{Overview}
What tests were performed etc...

\section{Agent performance against ANAC2011 agents.}
3a) Have your agent negotiate against itself, and against the three ANAC2011 agents HardHeaded,
Gahboninho, and TheNegotiator provided to you on the party domain. Run several negotiation
sessions using various utility profiles. Report on the outcomes reached. Try to explain why the
outcome is as it is. Are any of the outcomes a Nash solution? Is it possible to reach an efficient
outcome, i.e. an outcome that lies on the Pareto Frontier?

\section{Performance of the acceptance strategy}
3b) Test your agent in a small tournament while varying the acceptance strategy. Is there an acceptance
strategy which is better than your acceptance strategy?

\section{Performance of the opponent model}
3c) Test your agent in a small tournament and compare your opponent model with the original
HardHeaded frequency model. Does your model lead to a significantly higher utility?

\section{Application to other domains}
3d) One important question remains. How generic is your agent? That is, does it work as well
on the party domain as on other domains? To verify this, have your agent negotiate against
itself, and against at least three agents provided to you on at least three scenarios (for example,
Laptop, Grocery and ADG). Make sure your agent is able to deal with discounted domains.
Report on the outcomes reached. Try to explain why the outcome is as it is. Is any of the
outcomes a Nash solution? Is it possible to reach an efficient outcome, i.e. an outcome that lies
on the Pareto Frontier?